---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tveDataLoader)
```

# tveDataLoader

<!-- badges: start -->
<!-- badges: end -->

Load and perform basic data checks in a TVE manner.

## Installation

Install from github:

``` {r eval=FALSE}
renv::install("thevalueengineers/tveDataLoader")
```

## Example

`tve_path` converts paths to egnyte between Windows and MacOS formats.

``` {r}
# Run on MacOS:
tve_path("Z:/shared/TVE Data/1. Client Projects/")
```

`read_sav` is a wrapper around `haven::read_sav` that also converts all variable
names to lower case for consistency. Use it instead of `haven::read_sav` and try
to avoid loading the `haven` package into projects.

Load spss data with `read_sav` and `tve_path`:

```{r example, eval=FALSE}
library(tveDataLoader)
read_sav(
  paste0(
    tve_path(path_to_file),
    "filename.sav"
  )
)
```

`run_data_checks` performs basic data checks and exploration on your data.

``` {r}
tibble::tibble(
  respid = 1:10,
  weight = rep(1, 10),
  q1 = sample(1:5, 10, replace = TRUE)
) |> 
  run_data_checks()

```


