---
title: "Data Checking Report"
format: html
editor: visual
params:
  dat: `r jsonlite::toJSON(tibble::tibble(respid = 1))`
  unique_id: "unique_id"
  weight_var: "weight_var"
  weight_summary: tibble::tibble(variable = "weight",
                                 mean = 1,
                                 median = 1,
                                 var = 0,
                                 sd = 0,
                                 min = 1,
                                 max = 1,
                                 missing = integer(0),
                                 missing_percent = 0)
  vars_check: "vars_check"
---

```{r setup, echo=FALSE}
dat <- jsonlite::fromJSON(params$dat)
```

## Unique ID

`r ifelse(params$unique_id == "No unique ID", "No Unique ID identified", glue::glue("Unique ID: {params$unique_id}"))`

```{r echo = FALSE}
dplyr::select(params$dat, dplyr::all_of(params$unique_id))
```

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
